### 2023-04-24 Documentation/UFMG/PFCII/Apendices/ApendiceA.tex
documentation

\section{Machine Learn}

@@

@@

>>>>

\section{Machine Learning}

@@

\subsection{Neural Network with raw data}

@@

\begin{multicols}{2}

\begin{figure}[H]
    \center
    \includegraphics[width=7cm]{Figuras/spectogram/308_Dripping.png}
    \label{fig:spectrogram1}
    \caption{Dripping}
  \end{figure}

  \begin{figure}[H]
    \center
    \includegraphics[width=7cm]{Figuras/spectogram/486_Intermittent.png}
    \label{fig:spectrogram5}
    \caption{Dripping}
  \end{figure}

  \begin{figure}[H]
    \center
    \includegraphics[width=7cm]{Figuras/spectogram/94_Cone Jet.png}
    \label{fig:spectrogram2}
    \caption{Dripping}
  \end{figure}

  \begin{figure}[H]
    \center
    \includegraphics[width=7cm]{Figuras/spectogram/166_Multi Jet.png}
    \label{fig:spectrogram3}
    \caption{Dripping}
  \end{figure}

  \begin{figure}[H]
    \center
    \includegraphics[width=7cm]{Figuras/spectogram/276_Corona.png}
    \label{fig:spectrogram4}
    \caption{Dripping}
  \end{figure}

\end{multicols}

### 2023-04-24 Documentation/UFMG/PFCII/Results/Results.tex
documentation

        \begin{figure}[H]
            \center
            \includegraphics[width=8cm]{Figuras/report3/manual-mapping.png}
            \caption{ exp-26-01 manual classification}
        \end{figure}

@@

@@

        \begin{figure}[H]
            \center
            \includegraphics[width=12cm]{Figuras/19:03/non-dimensional-1.png}
            \caption{ exp-26-01-2 (V x Q)}
        \end{figure}

@@

    \subsection{Simple Controller}

        \begin{algorithm}
            \caption{simple controller}\label{alg:simple_controller}
            \begin{algorithmic}
            \Function{controller}{$spray\_mode$}

                \If{$spray\_mode$ = $'Intermittent'$ or $spray\_mode$ = $'Dripping'$}
                    \State \Call{send\_voltage\_command}{$voltage$ + 100}
                \ElsIf{$spray\_mode$ = $'Multi Jet'$ or $spray\_mode$ = $'Corona'$}
                    \State \Call{send\_voltage\_command}{$voltage$ - 100}
                \ElsIf{ $spray\_mode$ = $"Cone Jet"$}
                    \Comment{Keep Stable}
                \EndIf

            \EndFunction
            \end{algorithmic}
        \end{algorithm}

@@

        \begin{figure}[H]
            \center
            \includegraphics[width=15cm]{Figuras/19:03/control_first_results.png}
            \caption{ exp-26-01-2 (V x Q)}
        \end{figure}

>>>>

        \begin{figure}[H]
            \center
            \includegraphics[width=8cm]{Figuras/april/manual_stability.png}
            \caption{ exp-26-01 manual classification}
        \end{figure}

@@

        \begin{figure}[H]
            \center
            \includegraphics[width=8cm]{Figuras/april/results_map_1.png}
            \caption{ exp-26-01 manual classification}
        \end{figure}

        \begin{figure}[H]
            \center
            \includegraphics[width=9cm]{Figuras/april/results_map_2.png}
            \caption{ exp-26-01 automatic classification}
        \end{figure}

@@

        \begin{figure}[H]
            \center
            \includegraphics[width=7cm]{Figuras/april/manual_non_dim_exp.png}
            \caption{ exp-qw-01-2 (V x Q)}
        \end{figure}

        \begin{figure}[H]
            \center
            \includegraphics[width=10cm]{Figuras/19:03/non-dimensional-1.png}
            \caption{ exp-26-01-2 (V x Q)}
        \end{figure}

@@

@@

        \begin{figure}[H]
            \center
            \includegraphics[width=17cm]{Figuras/19:03/control_first_results.png}
            \caption{ exp-26-01-2 (V x Q)}
        \end{figure}
